## Uncomment and install packages if you don't have it
install.packages("tseries")
```{r}
library(knitr)
library(markdown)
library(tseries)
```
knit('SNP500.Rmd')


markdownToHTML("SNP500.md", "SNP500.html",fragment.only = TRUE)

## S&P 500 (^GSPC)
###    SNP - SNP Real Time Price. Currency in USD

# TODO: Download the data of SP500 '^gspc'.

```{r}
SNPdata <- get.hist.quote(instrument="^GSPC",quote="Close")
```
# TODO: Calculate the log returns, which is the subtractration of log(lag(SNPdata)) and log(SNPdata)
```{r}
SNPret <- log(lag(SNPdata)) - log(SNPdata)
```
# TODO: Calculate volatility measure that is to multiply sd(SNPret),sqrt(250), 100
```{r}
SNPvol <- sd(SNPret)*sqrt(250)*100
```

## Define getVol function for volatility
```{r}
getVol <- function(d, logrets) {
	var = 0
	lam = 0
	varlist <- c()

	for (r in logrets) {
		lam = lam*(1 - 1/d) + 1
	  var = (1 - 1/lam)*var + (1/lam)*r^2
		varlist <- c(varlist, var)
	}

	sqrt(varlist)
}
```

# Calculate volatility over entire length of series for various three different decay factors: 10 30. 100


```{r}
volest <- getVol(10,SNPret)
volest2 <- getVol(30,SNPret)
volest3 <- getVol(100,SNPret)
```

# Plot the results, overlaying the volatility curves on the data, just as was done in the S&P example.
```{r}
plot(volest,type="l")
lines(volest2, col="red", type="l")
lines(volest3, col="blue", type="l")
```
